\documentclass[english]{article}

\usepackage{babel}
\usepackage{graphicx}
\usepackage{alltt}
\usepackage{url}
%\usepackage{ngerman}
\usepackage{color}
\usepackage{framed}

\title{\huge\sffamily\bfseries Review of Group a by Group b}
\author{Loris Reiff \and Miro Haller \and Raphael Eikenberg \and Robertas Maleckas}
\date{\dots}


\begin{document}
\maketitle

%% **** please observe the page limit ****
%% (it is not allowed to change the font size or page geometry to gain more space!)
%% comment or remove lines below before hand-in
\begin{center}
{\large\textcolor{red}{Page limit: 18 pages.}}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tableofcontents
\pagebreak

\begin{framed}
\noindent
{\it
Recall the following guidelines when writing your reports:
\begin{itemize}
\item Adhere to the given templates.

\item Refer to the security principles in the book for justification.

\item Use clear terminology: 
\begin{itemize}
\item secure = confidential + authentic. Be clear about
which properties you are writing.
\item Are pairwise distinct: certificate, private key, public key, archive to of certificate with private key. Please avoid mixing these up.
\end{itemize}

\item Use a spell checker before hand-in!

\end{itemize}
}
\end{framed}


\section{Background}

\noindent {\bf Developers of the external system:} {\it x', y', z', ...} \\

\noindent {\bf Date of the review:} ...


\section{Report and Design Review}

Study the documentation that came with the external system and evaluation. 

\subsection{System Architecture and Security Concepts}

Is the chosen architecture well-suited for the tasks specified in the requirements? Are the security design decisions well motivated and justified? List positive and negative aspects for each question.


\subsection{Risk Analysis}

Is the risk analysis coherent and complete? That is, are all relevant assets, threat sources, and threats listed? 
%
Are the risk definitions (likelihood, impact, and risk) reasonable?
%
Are the countermeasures appropriate?


\section{Implementation Review}
 
\subsection{Compliance with Requirements} 

Does the system meet the functional and security requirements given in the assignment? Are they implemented correctly? If not, list any missing functionality or security measure.


\subsection{System Security Testing}

Systematically investigate the system. Are the countermeasures implemented as described? Do you see any security problems? Analyze the system using both black-box as well as white-box testing.


\subsection{Backdoors}

Describe all backdoors that you found on the system. It may be that you also find unintended backdoors (only the group's presentation will show whether they were intended or not).



\section{Comparison}

Compare your system with the external system you were given for the review. Are there any remarkable highlights in your system or the external system?


\end{document}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../../book"
%%% End: 
